\mireval{}

### 2014-05-09 paper/paper.tex
Better section title
Swapped ref by jsalamon's suggestion

In contrast to the tasks above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
As a result, we compared \mireval{}'s output on smaller development datasets for these tasks.
For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon2011melody} and compared \mireval{}'s reported scores to those of MIREX.
For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
We evaluated the estimated patterns using the MATLAB code released by Collins \cite{Collins2013}.
The number of algorithms, examples, and total number of scores for all tasks are summarized in Table \ref{tab:nexamples}.

@@

\section{Discussion}
\label{sec:discussion}

>>>>

In contrast to the tasks above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
As a result, we compared \mireval{}'s output on smaller development datasets for these tasks.
For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon:MelodyExraction:TASLP:12} and compared \mireval{}'s reported scores to those of MIREX.
For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
We evaluated the estimated patterns using the MATLAB code released by Collins \cite{Collins2013}.
The number of algorithms, examples, and total number of scores for all tasks are summarized in Table \ref{tab:nexamples}.

@@

\section{Towards Transparency and Community Involvement}
\label{sec:discussion}
